---
title: "Prediction Assignment Writeup"
output: 
  html_document:
    keep_md: true
---

## Data

The data for this project come from this source: 
http://groupware.les.inf.puc-rio.br/har.

The training data for this project are available here:
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here:
https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

Packages installed are:
#install.packages("caret")
#install.packages("randomForest")

## Loading the data
```{r}
library(caret)
library(randomForest)

training_data <- read.csv("pml-training.csv", na.strings=c("NA",""), strip.white=T)
testing_data <- read.csv("pml-testing.csv", na.strings=c("NA",""), strip.white=T)
```
## Clean the Data

Data is cleaned by removing the columns that contains NA and features that are not in testing dataset. We also remove the first 7 features since they are not numeric.
```{r}
features <- names(testing_data[,colSums(is.na(testing_data)) == 0])[8:59]
training_data <- training_data[,c(features,"classe")]
testing_data <- testing_data[,c(features,"problem_id")]

```
## Partitioning the dataset
```{r}
set.seed(12345)

inTrain <- createDataPartition(training_data$classe, p=0.6, list=FALSE)
training <- training_data[inTrain,]
testing <- training_data[-inTrain,]
```
## Building the Random Forest Model
```{r}
set.seed(12345) 
modelRandomForest <- randomForest(classe ~ ., data = training, ntree = 1000)
predictionRF <- predict(modelRandomForest, testing_data, type = "class")
```
## Predicting on the  Data
```{r}
predictonTrainData <- predict(modelRandomForest, newdata=training)
confusionMatrix(predictonTrainData,training$classe)


predictonTestData <- predict(modelRandomForest, newdata=testing)
confusionMatrix(predictonTestData,testing$classe)
```

## Conclusion

From the result of the confusion matrix , we can conclude that the  Random Forest model is very accurate, about 99%.. Because of that we could expect nearly all of the submitted test cases to be correct. 

